---
title: "RClub Presentation"
output:
  revealjs::revealjs_presentation:
    transition: none
    theme: simple
    highlight: pygments
    mathjax: local
    self_contained: false
    center: false
---
<!-- Hack via Githib issue to left align slide body content: 
    https://github.com/hakimel/reveal.js/issues/1897#issuecomment-301130888
-->
<style type="text/css">
  .reveal p {
    text-align: left;
  }
  .reveal ul {
    display: block;
  }
  .reveal ol {
    display: block;
  }
</style>

*Being an example of some of the things you can do after `install.packages("revealjs")`...*

`Tony.Hirst@open.ac.uk`

# Just Another Slide

We can use markdown:

- lists
  - sublists
- *emphasis*

etc.

# Rich Text

We can used styled code:

```R
fahrenheit_to_celsius <- function(temp_F) {
  temp_C <- (temp_F - 32) * 5 / 9
  return(temp_C)
}
```

## And subslides...
And LaTeX equations: 

\begin{align*}
  f(x) &= x^2\\
  g(x) &= \frac{1}{x}\\
  F(x) &= \int^a_b \frac{1}{3}x^3
\end{align*}

# Code outputs

We can embed code output:

```{r}
a<-1
a+1
```

# Widget Output

We can hide the code as per normal and just embed output:

```{r, echo=FALSE}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m

```